Supermassive black holes and their host spheroids \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram

### 2015-10-16 papers/data_paper/ApJ_submission_2/replytoreferee_I.txt

Dear Lee,

The referee's comments and suggestions have been very useful and helped improve the quality of the manuscript. 
We have addressed all the points listed in the reviewer's report. Below are our responses to the report. 
The title of the paper has been modified, as suggested by the referee, and all changes to the text have been printed 
in bold face.

Kind regards,

Giulia Savorgnan

RESPONSES TO THE REVIEWER'S REPORT:

@@

- The tone of the title was not meant to be presumptuous, but we now understand that it is prone to misinterpretation, 
  therefore we have modified it. The new title reads: "Galaxy vivisection".

- We agree that some disk galaxies, like NGC 300, can be bulge-less. However, all galaxies in our sample are either 
  ellipticals/lenticulars or early-type spirals (Sa-Sc), with the only exception of NGC 4945 (Scd). 
  By definition, these galaxies have a spheroid/bulge component, which is what we modelled with a Sersic profile, 
  without attempting to distinguish between classical and pseudo-bulges. The text in Section 3.5 was actually misleading 
  and has been modified.
  Throughout the text, we used the terms "spheroid" and "bulge" as synonyms, although we recognize that some bulges are 
  "disk-like" rather than "spheroidal-like". This point has now been clarified in Footnote 1.

- We did not attempt to fit down- or up-bendings of large-scale disks. We scrutinized the available literature for all 
  individual galaxies, and we paid particular attention to the papers that recorded disk breaks. 
  The surface brightness profiles of galaxies that present this feature were truncated well before the occurrence of the 
  bending. This was not explicit in the text, and we have now added a sentence at the end of Section 3.1.

- The 1D equivalent axis fit does account for the varying ellipticity because the equivalent axis is calculated as 
  Req = Rmaj * (1-ellipticity)^0.5. 
  M87 has a strong ellipticity gradient. The 2D model cannot account for this gradient, and this can be seen in the 2D 
  residual image which looks like a "butterfly pattern". 
  Ideally, galaxies should be fit in 3D, rather than 2D or 1D. However, because the 1D fit tracks the changes in the 
  observed P.A. and ellipticity, the geometric mean axis (equivalent to a circularized axis) enables one to accurately 
  recover the total and component magnitudes in a way that the 2D model cannot.

@@

- The text in Section 3.5 was not accurate, and we have now clarified this point. All bars have been fit with a Ferrer function, 
  except for NGC 4151 where we preferred to use a Sersic model. Disk-like components embedded in the bulges/spheroids have 
  been fit with a low-n Sersic profile and, in a few cases (when the Sersic model was degenerate with the other model-
  components), with a Ferrer function. 
  Gadotti & De Souza (2006) report that flat bars are typical of earlier type spirals, whereas exponential bars are common 
  in later type spirals. This is in agreement with our findings: our galaxy sample lacks of later-type spirals and we did 
  not detect any bar with an exponential profile.

- Sheth et al. (2010, the paper that presents the S4G collaboration) refers to Jun & Im (2008) to point out that the 3.6 um
  band is indeed a better tracer of the stellar mass than the K-band, which still suffers from dust absorption (Driver et al.
  2008, 678, L101).

- In Figure 7 we compared the 2D Sersic indices with the 1D equivalent-axis Sersic indices. These two quantities are not 
  expected to be exactly the same, but they should be approximatively similar. There are four most obvious outliers in this 
  plot: NGC 821, NGC 3377, NGC 4945, and NGC 5576. Their individual cases are discussed in the Appendix. 
  For M87, the 2D Sersic index (4.3) and the 1D equivalent-axis Sersic index (5.9) are in fairly good agreement. 
  The large discrepancy between the M87's 1D major-axis Sersic index and the other two measurements is due to the strong ellipticity
  gradient that this galaxy has. In fact, the 2D model cannot account for such gradient (whereas the 1D equivalent-axis fit can) 
  and the 2D residuals show a significant ``butterfly'' feature caused by this well-understood problem.

- The aim of this work is to investigate scaling relations between the black hole mass, Mbh, and several properties, X, of the host 
  spheroid/bulge. These correlations are commonly expressed as power laws: Mbh \propto X^a, i.e. log(Mbh) = a*log(X) + b. 
  Therefore we are interested in the logarithmic values of the Sersic indices and effective radii, along with their associated 
  uncertainties. 
  In addition, the Sersic index is the "exponent" in the Sersic equation, and that one needs to deal with the log of this quantity.  
  A fixed change in n is very different depending on the value of n, for example 2+/-1 results in a much greater change to the profile 
  than 10+/-1.

@@

- The point that Footnote 2 was trying to make is the following. Sani et al., Vika et al. and Beifiori et al. did not find a 
  correlation between black hole mass and Sersic index. However, after averaging their Sersic indices together, a strong correlation
  was recovered. This is telling us that the measurements obtained by the individual authors were "noisy", i.e. non accurate. 
  Averaging the Sersic indices together reduces the noise and shows that the black hole mass is indeed correlated to the Sersic 
  index. However, we removed the second sentence of Footnote 2; we will come back to this point in a future paper.

- The claim about the anti-truncation of NGC 4459 has been clarified in the Appendix.

- Thanks for pointing out the missing reference to Erwin & Gadotti (2012), which has now been added.

- The Spitzer cookbook does not explain why the overlap correction is not recommended for 3.6 um images, it just states so. 
  It might be that the cookbook does not consider mosaicking images belonging to different "Astronomical Observation Requests", 
  for which we found that the overlap correction was needed to remove the chess-board effect.

@@

- Section 4.2.1, item 2: the typo has been corrected.

- Section 4.2.2: a sentence has been added to explain the different sigma symbols.

- The edge-on disc of NGC 1332 is clearly identified in the galaxy image. The ellipticity profile of the galaxy isophotes indicates 
  that the disc is intermediate-scale. We modified the caption of Figure 35 to better illustrate this point.

- The fifth paragraph of Section 3.5 explains how we decided to include a nuclear component in our models.

- We tried to model the bar of NGC 4945 with a Ferrer function or a Sersic model, but we did not obtain a satisfactory result. 
  We now realize that NGC 4945 is the only later type (Scd) spiral galaxy in our sample, and its bar might not be well described 
  by a Ferrer function. However, a Sersic model did not provide a good fit of the bar either. It is likely that the edge-on 
  inclination of the galaxy complicated the extraction of the surface brightness profile with ELLIPSE. 
  Our best solution is still to exclude the data in the range where the bar dominates the light and model only the bulge and the 
  large-scale disk. We note that we classified the fit of this galaxy as "grade 2".

@@

- Kormendy & Ho (2013) did not perform bulge/disk decompositions for their galaxies, but they collected results from various sources 
  in the literature. We wanted to compare the results from our decompositions with the results from other systematic studies that 
  performed galaxy modelling in a consistent way.

And finally, I'd like to say thanks for the kind words at the beginning of the report. 
It is actually "refreshing" for myself to see that our effort is acknowledged by someone that fully understands the problematic 
involved in galaxy decomposition, so thanks a lot for the encouragement!

### 2015-10-16 papers/MbhMsph/ApJ_submission/mm.tex
grampians

%\title{Supermassive black hole and host bulge affairs \\ II. The early and late sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}
\title{Supermassive black hole and host spheroid affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}

%\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1} and A. Marconi and E. Sani\altaffilmark{3} and L.K. Hunt}
%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
%\email{gsavorgn@astro.swin.edu.au}

@@

%It should also be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
%and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies (lenticulars and spirals). \\
%Several recent papers \citep{jiang2011a,jiang2013,mathur2012,reines2013} claimed an offset at the low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ diagram,
%such that the black hole mass is lower than expected from the near-linear correlation traced by the high-mass, early-type spheroids. 
%However, \cite{grahamscott2013} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
%are not randomly offset from such near-linear correlation, 
%but follow the steeper relation traced by the S\'ersic spheroids. 
%Using bulge/disk decomposition data from \cite{jiang2011a}, 
%\cite{grahamscott2015} derived the host spheroid masses 
%and showed that the steeper $M_{\rm BH} - M_{\rm *,sph}$ extends to these spheroids with even lower black hole masses 
%($10^{5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 2 \times 10^{6}$), 
%and a more detailed analysis will be presented in Graham et al. (2015, \emph{in preparation}).  \\

@@

\subsection{Black hole mass -- galaxy luminosity}
The $M_{\rm BH} - L_{\rm gal}$ diagram is shown in Figure \ref{fig:mbhmaggal}.
Four spiral galaxies had their total luminosities underestimated (see Table \ref{tab:sample}) 
and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
\cite{lasker2014anal} analyzed a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
and claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
That is, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
However, our $M_{\rm BH} - L_{\rm sph}$ relation for all 66 galaxies, irrespective of their morphological type, 
has an intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas our $M_{\rm BH} - L_{\rm gal}$ relation for 62 ($=66-4$) galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the size of the uncertainties associated with the absolute magnitudes\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our conclusion by increasing the uncertainties associated with the galaxy absolute magnitudes\footnote{The 
value of the intrinsic scatter obviously depends also on the size of the uncertainties associated with the black hole masses. 
However, black hole masses and their uncertainties have been estimated by various authors using different methods, 
thus we have limited to no control on their values.}  
(we originally assumed $0.25\rm~mag$).
The intrinsic scatter of the $M_{\rm BH} - L_{\rm gal}$ relation only becomes smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation 
when assuming an uncertainty larger than $0.7\rm~mag$ for $L_{\rm gal}$, 
which would be significantly larger than the typical value commonly recognized in the literature, 
and would also oddly exceed the typical uncertainty that we estimated for $L_{\rm sph}$. 
Hence, we conclude that our determination of the relative intrinsic scatter is reliable, 
and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies\footnote{The majority 
of our early-type galaxies are elliptical galaxies, some of which have a bulge-to-total ratio close to 1 ($L_{\rm gal} \simeq L_{\rm sph}$).
One might wonder whether this constitutes a bias in our analysis.
However, we checked that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ 
not only for early-type (elliptical + lenticular) galaxies, 
but also for lenticular galaxies only. }, 
but not for all (early+late-type) galaxies.
%We decided to vary only the errors associated to $L_{\rm gal}$ 
%because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
%that takes into account the systematic errors related to the galaxy decomposition process. 
%We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
%have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
%Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
%and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
%we conclude that our determination of the intrinsic scatter is reliable, 
%and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
%As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
%than performing accurate galaxy decompositions to obtain bulge luminosities. 
%This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
%to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ diagram.}
\begin{tabular}{llccccc}
\tableline\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm gal} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - \langle MAG_{\rm gal} \rangle)/{\rm mag}]$} \\ [0.5em]
 All (62)               & BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\ [0.5em]
                        & BCES $(X|Y)$   & $8.26 \pm 0.12$ & $-1.01 \pm 0.15$ & $-24.78$ & $-$ & $0.92$ \\
                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\ [0.5em]
                        & BCES Bisector  & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
                        & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.15$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]

 Early-type (E+S0) (45) & BCES $(Y|X)$   & $8.56 \pm 0.07$ & $-0.44 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
                        & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\ [0.5em]
                        & BCES $(X|Y)$   & $8.56 \pm 0.08$ & $-0.64 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
                        & mFITEXY $(X|Y)$  & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.07}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\ [0.5em]
                        & BCES Bisector  & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
                        & mFITEXY Bisector & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.10$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]

%Late-type (Sp) (13) & BCES $(Y|X)$      & $7.37 \pm 0.17$ & $-0.33 \pm 0.87$   & $-24.39$ & $-$ & $0.65$ \\
%                    & BCES $(X|Y)$      & $7.37 \pm 1.97$ & $-21.66 \pm 53.74$ & $-24.39$ & $-$ & $7.73$ \\
%                    & BCES Bisector     & $7.37 \pm 0.20$ & $-1.32 \pm 0.94$   & $-24.39$ & $-$ & $0.77$ \\
%                    & FITEXY $(Y|X)$    & $7.38^{+0.17}_{-0.18}$ & $-0.34^{+0.74}_{-0.80}$ & $-24.39$ & $0.63^{+0.19}_{-0.11}$ & $0.65$ \\
%                    & FITEXY $(X|Y)$    & $$ & $$ & $-24.39$ & $$ & $$ \\
%                    & FITEXY Bisector   & $$ & $$ & $-24.39$ & $-$    & $$ \\
%                    & {\tt linmix\_err} $(Y|X)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
%                    & {\tt linmix\_err} $(X|Y)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
%                    & {\tt linmix\_err} Bisector    & $$ & $$ & $-24.39$ & $-$    & $$ \\

%All (62)               & BCES $(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
%                       & BCES $(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
%                       & BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
%                       & FITEXY $(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
%                       & FITEXY $(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
%                       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
%                       & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\
%                       & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\
%                       & {\tt linmix\_err} Bisector    & $$ & $$ & $$ & $-$    & $$ \\

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
All (66)               & BCES $(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
                       & mFITEXY $(Y|X)$    & $8.17^{+0.06}_{-0.07}$ & $-0.43^{+0.03}_{-0.04}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
                       & {\tt linmix\_err} $(Y|X)$     & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\ [0.5em]
                       & BCES $(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
                       & mFITEXY $(X|Y)$    & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.68$ \\
                       & {\tt linmix\_err} $(X|Y)$     & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\ [0.5em]
                       & BCES Bisector  & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
                       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
                       & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.09$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]

>>>>

\title{Supermassive black holes and their host spheroids \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram}

@@

@@

\subsection{Black hole mass -- galaxy luminosity}
The $M_{\rm BH} - L_{\rm gal}$ diagram is shown in Figure \ref{fig:mbhmaggal}.
Four spiral galaxies had their total luminosities underestimated (see Table \ref{tab:sample}) 
and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
\cite{lasker2014anal} analyzed a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
and claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
That is, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
However, our $M_{\rm BH} - L_{\rm sph}$ relation for all 66 galaxies, irrespective of their morphological type, 
has an intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas our $M_{\rm BH} - L_{\rm gal}$ relation for 62 ($=66-4$) galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
Because the value of the intrinsic scatter depends on the size of the uncertainties associated with the absolute magnitudes\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our conclusion by increasing the uncertainties associated with the galaxy absolute magnitudes\footnote{The 
value of the intrinsic scatter obviously depends also on the size of the uncertainties associated with the black hole masses. 
However, black hole masses and their uncertainties have been estimated by various authors using different methods, 
thus we have limited to no control on their values.}  
(we originally assumed $0.25\rm~mag$).
The intrinsic scatter of the $M_{\rm BH} - L_{\rm gal}$ relation only becomes smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation 
when assuming an uncertainty larger than $0.7\rm~mag$ for $L_{\rm gal}$, 
which would be significantly larger than the typical value commonly recognized in the literature, 
and would also oddly exceed the typical uncertainty that we estimated for $L_{\rm sph}$. 
Hence, we conclude that our determination of the relative intrinsic scatter is reliable, 
and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies\footnote{The majority 
of our early-type galaxies are elliptical galaxies, some of which have a bulge-to-total ratio close to 1 ($L_{\rm gal} \simeq L_{\rm sph}$).
One might wonder whether this constitutes a bias in our analysis.
However, we checked that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ 
not only for early-type (elliptical + lenticular) galaxies, 
but also for lenticular galaxies only. }, 
but not for all (early+late-type) galaxies.

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ diagram.}
\begin{tabular}{llccccc}
\tableline\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm gal} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - \langle MAG_{\rm gal} \rangle)/{\rm mag}]$} \\ [0.5em]
 All (62)               & BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\ [0.5em]
                        & BCES $(X|Y)$   & $8.26 \pm 0.12$ & $-1.01 \pm 0.15$ & $-24.78$ & $-$ & $0.92$ \\
                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\ [0.5em]
                        & BCES Bisector  & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
                        & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]

 Early-type (E+S0) (45) & BCES $(Y|X)$   & $8.56 \pm 0.07$ & $-0.44 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
                        & mFITEXY $(Y|X)$  & $8.56^{+0.06}_{-0.06}$ & $-0.42^{+0.05}_{-0.05}$ & $-24.88$ & $0.41^{+0.06}_{-0.05}$ & $0.45$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.43 \pm 0.06$ & $0.45$ \\ [0.5em]
                        & BCES $(X|Y)$   & $8.56 \pm 0.08$ & $-0.64 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
                        & mFITEXY $(X|Y)$  & $8.56^{+0.08}_{-0.08}$ & $-0.66^{+0.07}_{-0.08}$ & $-24.88$ & $0.51^{+0.07}_{-0.06}$ & $0.55$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.56 \pm 0.09$ & $-0.65 \pm 0.08$ & $-24.88$ & $0.53 \pm 0.10$ & $0.54$ \\ [0.5em]
                        & BCES Bisector  & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
                        & mFITEXY Bisector & $8.56^{+0.07}_{-0.07}$ & $-0.54^{+0.06}_{-0.06}$ & $-24.88$ & $-$    & $0.47$ \\
                        & {\tt linmix\_err} Bisector & $8.56 \pm 0.08$ & $-0.53 \pm 0.05$ & $-24.88$ & $-$    & $0.47$ \\ [0.5em]

@@

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$ diagram.}
\begin{tabular}{llccccc}
\tableline
\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - \langle MAG_{\rm sph} \rangle)/{\rm mag}]$} \\ [0.5em]
All (66)               & BCES $(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
                       & mFITEXY $(Y|X)$    & $8.17^{+0.06}_{-0.07}$ & $-0.43^{+0.03}_{-0.04}$ & $-23.86$ & $0.49^{+0.06}_{-0.05}$ & $0.56$ \\
                       & {\tt linmix\_err} $(Y|X)$     & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\ [0.5em]
                       & BCES $(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
                       & mFITEXY $(X|Y)$    & $8.15^{+0.07}_{-0.08}$ & $-0.61^{+0.05}_{-0.05}$ & $-23.86$ & $0.58^{+0.07}_{-0.06}$ & $0.68$ \\
                       & {\tt linmix\_err} $(X|Y)$     & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.60 \pm 0.09$ & $0.67$ \\ [0.5em]
                       & BCES Bisector  & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
                       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
                       & {\tt linmix\_err} Bisector    & $8.16 \pm 0.08$ & $-0.51 \pm 0.03$ & $-23.86$ & $-$    & $0.59$ \\ [0.5em]

$n>2$ (43)             & BCES $(Y|X)$      & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
                       & mFITEXY $(Y|X)$    & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38^{+0.06}_{-0.06}$ & $0.46$ \\
                       & {\tt linmix\_err} $(Y|X)$     & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.40 \pm 0.06$ & $0.46$ \\ [0.5em]
                       & BCES $(X|Y)$      & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
                       & mFITEXY $(X|Y)$    & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.44^{+0.08}_{-0.11}$ & $0.55$ \\
                       & {\tt linmix\_err} $(X|Y)$     & $8.55 \pm 0.09$ & $-0.57 \pm 0.08$ & $-24.77$ & $0.49 \pm 0.10$ & $0.55$ \\ [0.5em]
                       & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
                       & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
                       & {\tt linmix\_err} Bisector    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.77$ & $-$    & $0.49$ \\  [0.5em]
